Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-04 workflow/workflow.Rmd
edits in DESCRIPTION

[FP: we need to have only 8 keywords, which ones do you prefer? SD: I selected 8, please check.]

@@

- solve loading packages issues (DR), DONE!
- versions of packages we want to use in develop branches and change functions in text accordingly (EP and DR), [DR: scone and zinbwave now OK!]
- update clustering section with new clusterExperiment functions (EP),
- add details in section preprocessing (DR),
- address Sandrine's comments in sections slingshot and de (KS),
- clean up singlecellworkflow package (FP),
- update NAMESPACE and DESCRIPTION (FP),
- install and run package using cache instead of saved files for zinbwave and clusterExperiment and making sure we can build the vignette using R 3.4 and bioc-devel 3.6 (all?),
- make singlecellworkflow package public (FP).]

@@

```{r tree, fig.cap="Cells color-coded by cluster in a 4-dimensional MDS space with connecting lines between cluster centers representing the inferred structure."}
pairs(lineages, type='lineages', col = pal[primaryClusterNamed(ceObj)])
```

@@

pairs(lineages, type='curves', col = pal[primaryClusterNamed(ceObj)])
```

@@

```{r slingshotsupervised, eval=FALSE}
lineages <- getLineages(X, clusterLabels = cl, start.clus = "c1",
                         end.clus = c("c3", "c6"))
lineagees <- getCurves(lineages)
pairs(lineages, type='curves', col = pal[primaryClusterNamed(ceObj)])
pairs(lineages, type='lineages', col = pal[primaryClusterNamed(ceObj)], show.constraints = TRUE)

>>>>

@@

- solve loading packages issues (DR), DONE!
- versions of packages we want to use in develop branches and change functions in text accordingly (EP and DR), [DR: scone and zinbwave now OK!]
- update clustering section with new clusterExperiment functions (EP),
- add details in section preprocessing (DR), DONE,
- address Sandrine's comments in sections slingshot and de (KS),
- try running workflow with more genes (FP),
- plot gene variance density (FP),
- clean up singlecellworkflow package (FP),
- update NAMESPACE and DESCRIPTION (FP),
- install and run package using cache instead of saved files for zinbwave and clusterExperiment and making sure we can build the vignette using R 3.4 and bioc-devel 3.6 (all?),
- make singlecellworkflow package public (FP).]

@@

```{r tree, fig.cap="Cells color-coded by cluster in a 4-dimensional MDS space with connecting lines between cluster centers representing the inferred structure."}
pairs(lineages, type="lineages", col = pal[primaryClusterNamed(ceObj)])
```

@@

pairs(lineages, type="curves", col = pal[primaryClusterNamed(ceObj)])
```

@@

```{r slingshotsupervised, eval=FALSE}
lineages <- getLineages(X, clusterLabels = cl, start.clus = "c1",
                         end.clus = c("c3", "c6"))
lineagees <- getCurves(lineages)
pairs(lineages, type="curves", col = pal[primaryClusterNamed(ceObj)])
pairs(lineages, type="lineages", col = pal[primaryClusterNamed(ceObj)], show.constraints = TRUE)
